SST_patterns

### 2020-01-31 SST_patterns.Rmd
update

Complete_mean_intensity <- rbind(CMC_binding,OISST_binding, G1SST_binding, MUR_binding) %>% 
  ungroup() %>% 
  select(-heading, - distance, -distance_km)

>>>>

Complete_mean_intensity <- rbind(CMC_binding,OISST_binding, G1SST_binding, MUR_binding) %>% 
  ungroup() %>% 
  select(-heading, - distance, -distance_km) # Here I remove distance, Keep if distance is needed
